Visualizing Example of Clustered Predicted TAD Boundary Regions

### 2019-08-23 Scripts/evaluating_rfe_across_chromosomes.Rmd
edits

@@

#gm12878
rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
rfegm12878 <- reshape(rfegm12878[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfegm12878)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfegm12878.mat <- as.matrix(rfegm12878[,-1])
rownames(rfegm12878.mat) <- rfegm12878$Feature
rfegm12878.mat[is.na(rfegm12878.mat)] <- 0
rfegm12878.mat <- apply(rfegm12878.mat,2,rev)

#using heatmap.2
distance.col = dist(rfegm12878.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfegm12878.mat))
heatmap.2(t(rfegm12878.mat),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1.5,
          cexCol=1.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfegm12878.mat)),
          colsep=0:ncol(t(rfegm12878.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```

>>>>

```{r}
rfeperchr <- data.frame()

@@

```

#### GM12878

rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
rfegm12878 <- reshape(rfegm12878[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfegm12878)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfegm12878.mat <- as.matrix(rfegm12878[,-1])
rownames(rfegm12878.mat) <- rfegm12878$Feature
rfegm12878.mat[is.na(rfegm12878.mat)] <- 0
rfegm12878.mat <- apply(rfegm12878.mat,2,rev)

#using heatmap.2
distance.col = dist(rfegm12878.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfegm12878.mat))
heatmap.2(t(rfegm12878.mat),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfegm12878.mat)),
          colsep=0:ncol(t(rfegm12878.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```

#### K562

```{r}
rfek562 <- rfeperchr[which(rfeperchr$CL=="K562"),]
rfek562 <- reshape(rfek562[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfek562)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfek562.mat <- as.matrix(rfek562[,-1])
rownames(rfek562.mat) <- rfek562$Feature
rfek562.mat[is.na(rfek562.mat)] <- 0
#rfek562.mat <- apply(rfek562.mat,2,rev)

#using heatmap.2
distance.col = dist(rfek562.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfek562.mat))
heatmap.2(t(rfek562.mat),
          #labRow=rownames(rfek562.mat),
          #labCol=colnames(rfek562.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfek562.mat)),
          colsep=0:ncol(t(rfek562.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```

### 2019-08-23 Scripts/visualizing_example_predicted_tad_bounds.Rmd
edits

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(factoextra)
```

@@

###17390000-18640000

```{r}
called_and_pred_bound_regions <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bound_regions.rds")

predprob_df_1 <- called_and_pred_bound_regions[[1]]
predprob_df <- called_and_pred_bound_regions[[2]]
trueBound_gr_region <- called_and_pred_bound_regions[[3]]
predBound_gr <- called_and_pred_bound_regions[[4]]

predprob_df$baseNum[which(predprob_df$trueBound=="Yes")][1:10]
#17390000 17540000 17550000 17650000 17820000 18010000 18030000 18210000 18280000 18640000

predprob_df_temp <- predprob_df[which(predprob_df$baseNum>=17390000 & predprob_df$baseNum<=18640000),]
table(predprob_df_temp$predBound)

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
	              color="blue", 
	              #linetype="dashed", 
	              size=.5)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

x <- dist(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], method = "euclidean")

xlabels <- c("1", "2", "3", "9", "10", "4", "5", "8", "6", "7")
fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("")+
  ylab("")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance",
                       low = "white", 
                       mid = "pink",
                       midpoint = 450000,
                       high = muted("red"))+
  scale_x_discrete(labels=xlabels)+
  scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

hc1 <- hclust(x, method = "complete")
plot(hc1)

z <- sapply(2:(dim(as.matrix(x))[1]-1), function(i) { 
    mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
plot(2:(dim(as.matrix(x))[1]-1), z)

k = which.max(z)+1
p <- pam(x, diss=TRUE, k=k, cluster.only=TRUE, trace.lev = 0)
clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=cutree(hc1, k=k))

plot(hc1, hang = -1)
rect.hclust(hc1, k = k)

prob1intervals <- unique(clustdf$clust)
  mid2 <- numeric()
  for(i in prob1intervals){
    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
    n=dim(dat)[1]
    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
  }

  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% mid2, "Yes", "No")

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
	              color="blue", 
	              #linetype="dashed", 
	              size=1)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(factoextra)
library(dendextend)
```

@@

###17380000-18650000 (first 10 called TAD boundaries)

```{r}
#GM12878
#CHR22

#reading in probability vector
pred.TADModel <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/pred.TADModel.rds")

#reading in called and predicted TAD boundary regions
called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bounds.rds"))

#assigning called tad boundaries
called <- called_and_pred[[1]]
called <- resize(called, width=1,fix = "center")

#assigning predicted tad boundaries
predicted <- called_and_pred[[2]]

#reading in base pair data for chromosome 22
seqData <- readRDS("Z:/TAD_data_analysis/seq_data/seqData_CHR22.rds")

#creating a dataframe with base pair coordinates, what the probability of each base pair being a TAD boundary, and which base pair corresponds to a called tad boundary
predprobdata <- data.frame(basenum = seqData,
                           prob = pred.TADModel,
                           called = ifelse(seqData %in% start(called), "Yes", "No"))
dim(predprobdata) #48284564        4

rm(seqData)
rm(pred.TADModel)
rm(called_and_pred)

start(called)[1:10]
#17389999 17539999 17549999 17649999 17819999 18009999 18029999 18209999 18279999 18639999

#creating a window from the first called tad boundary to the 10th called tad boundary (+- 10000 bp)
s=start(called)[1:10][1]-10000+1
e=start(called)[1:10][10]+10000+1

predprobdata2 <- predprobdata[which(predprobdata$basenum>=s & predprobdata$basenum <= e), ]
dim(predprobdata2) #1270001       3

#datasets for plotting
##only called boundaries
calleddata <- predprobdata2[which(predprobdata2$called=="Yes"),]
dim(calleddata) #10  3
##only predicted tad regions (p=1)
predicteddata <- predprobdata2[which(predprobdata2$prob==1),]
dim(predicteddata) #20055     3

#plot
ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                            color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                  color="red"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "red"),
                     labels = c("Called Boundary", 'Predicted Region'))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

#determine midpoints of predicted tad regions
prob1basenumdiff <- diff(predicteddata$basenum)
retain <- numeric()
x <- 1
for(i in 1:length(prob1basenumdiff)){
  if(prob1basenumdiff[i]<=1){retain[i] = x}else{x = x+1; retain[i] = x}
}
retain = c(1,retain)
length(table(retain)) #95

mid <- numeric()
for(i in unique(retain)){
  #print(i)
  bpdat <- predicteddata$basenum[which(retain==i)]
  n=length(bpdat)
  mid[i] <- ceiling((bpdat[1]+bpdat[n])/2)
}

#create distance matrix of all pairwise distances between midpoints
x <- dist(mid, method = "euclidean")

#visualize distance matrix
fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("Predicted Boundary Regions")+
  ylab("Predicted Boundary Regions")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance\nBetween\nMidpoints",
                       low = "white", 
                       mid = "pink",
                       midpoint = 600000,
                       high = muted("red"),
                       limits=c(0,1200000),
                       breaks=c(0,400000, 800000, 1200000),
                       labels=c("0","400000", "800000", "1200000"))+
  #scale_x_discrete(labels=xlabels)+
  #scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

#cluster distance matrix
hc1 <- hclust(x, method = "complete")
plot(hc1)

#determine suitable number of clusters using the silhouette method
z <- sapply(2:(length(mid)-1), function(i) { 
  mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
k=which.max(z)+1
k #10

#perform PAM clustering to determine cluster centers
c <- clara(mid, 
           k=k, 
           samples=100,
           metric = "euclidean",
           stand = FALSE, 
           trace = 2, 
           medoids.x = TRUE)
clustdf <- data.frame(mid=mid, 
                      clust=c$clustering, 
                      medoid=ifelse(mid %in% c$medoids, "Yes", "No"))

dend <- as.dendrogram(hc1)
dend %>% set("labels_colors", 
             value=as.numeric(clustdf$medoid)+1) %>% 
  set("labels_cex", value=1.5) %>% 
  plot(main = "Clustered Distances", xlab="Predicted Boundary Regions")
rect.hclust(hc1, k = k)

#assign cluster centers as predicted TAD boundaries
predprobdata2$predicted <- ifelse(predprobdata2$basenum %in% clustdf$mid[which(clustdf$medoid=="Yes")], "Yes", "No")

predicteddata2 <- predprobdata2[which(predprobdata2$predicted=="Yes"),]

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                     color="green"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "green", "red"),
                     labels = c("Called Boundary",
                                "Predicted Boundary",
                                "Predicted Region"))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

## CHR22

### 17390000-18640000 (first called TAD on chr 22; 2 boundaries)

```{r}
domains <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt", header=F)
resolution=as.integer(10000)
preprocess=TRUE
domains.mat=domains
domains.mat <- domains.mat[,1:3]
domains.mat[,1] <- paste0("chr",domains.mat[,1])
colnames(domains.mat) <- c("Chromosome", "Start", "End")
if(preprocess==TRUE){
  ##restricting domain data to TADs > 2*resolution and < 2,000,000
  domains.mat <- domains.mat[which((domains.mat$End - domains.mat$Start)>(2*resolution) & (domains.mat$End - domains.mat$Start)<2000000),]
}

head(domains.mat[which(domains.mat$Chromosome=="chr22"),])
d <- domains.mat[which(domains.mat$Chromosome=="chr22"),]
head(d[order(d$Start, decreasing = FALSE),])
d <- d[order(d$Start, decreasing = FALSE),]

s=d$Start[1]-1000
e=d$End[2]+1000
predprobdata2 <- predprobdata[which(predprobdata$basenum>=s & predprobdata$basenum <= e), ]
dim(predprobdata2) #152001      3

calleddata <- predprobdata2[which(predprobdata2$called=="Yes"),]
dim(calleddata) #2 3

predicteddata <- predprobdata2[which(predprobdata2$prob==1),]
dim(predicteddata) #3471    3

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "red"),
                     labels = c("Called Boundary", 'Predicted Region'))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

prob1basenumdiff <- diff(predicteddata$basenum)
retain <- numeric()
x <- 1
for(i in 1:length(prob1basenumdiff)){
  if(prob1basenumdiff[i]<=1){retain[i] = x}else{x = x+1; retain[i] = x}
}
retain = c(1,retain)
length(table(retain)) #20

mid <- numeric()
for(i in unique(retain)){
  #print(i)
  bpdat <- predicteddata$basenum[which(retain==i)]
  n=length(bpdat)
  mid[i] <- ceiling((bpdat[1]+bpdat[n])/2)
}

x <- dist(mid, method = "euclidean")

fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("Predicted Boundary Regions")+
  ylab("Predicted Boundary Regions")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance\nBetween\nMidpoints",
                       low = "white", 
                       mid = "pink",
                       midpoint = 75000,
                       high = muted("red"),
                       limits=c(0,150000),
                       breaks=c(0,50000,100000,150000),
                       labels=c("0","50000", "100000", "150000"))+
  #scale_x_discrete(labels=xlabels)+
  #scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

hc1 <- hclust(x, method = "complete")
plot(hc1)
z <- sapply(2:(length(mid)-1), function(i) { 
  mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
k=which.max(z)+1
k #2

c <- clara(mid, 
           k=k, 
           samples=100,
           metric = "euclidean",
           stand = FALSE, 
           trace = 2, 
           medoids.x = TRUE)
clustdf <- data.frame(mid=mid, 
                      clust=c$clustering, 
                      medoid=ifelse(mid %in% c$medoids, "Yes", "No"))

dend <- as.dendrogram(hc1)
dend %>% set("labels_colors", 
             value=as.numeric(clustdf$medoid)+1) %>% 
  set("labels_cex", value=1.5) %>% 
  plot(main = "Clustered Distances", xlab="Predicted Boundary Regions")
rect.hclust(hc1, k = k)

predprobdata2$predicted <- ifelse(predprobdata2$basenum %in% clustdf$mid[which(clustdf$medoid=="Yes")], "Yes", "No")

predicteddata2 <- predprobdata2[which(predprobdata2$predicted=="Yes"),]

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="green"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "green", "red"),
                     labels = c("Called Boundary",
                                "Predicted Boundary",
                                "Predicted Region"))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
